Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2020-04-03 thirdPaper/draft/typeConeAssociahedra.tex

The type cone of~$\gvectorFan[2]$ lives in~$\R^9$ and has a linearity space of dimension~$3$.
It has $6$ facet-defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititiesAsso}\,(right).

@@

In~\cite{Auslander1984}, M.~Auslander showed that the relations in the Grothendieck group of an Artin algebra are generated by the ones given by almost-split sequences precisely when the algebra is of finite representation type. Inspired by this result, we will show that a similar statement holds (see \cref{thm:relations-g-vecteurs}) for the~$\b{g}$-vectors (or indices) of objects in a~$2$-Calabi--Yau triangulated category.

>>>>

The type cone of~$\gvectorFan[3]$ lives in~$\R^9$ and has a lineality space of dimension~$3$.
It has $6$ facet-defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititiesAsso}\,(right).

@@

In~\cite{Auslander1984}, M.~Auslander showed that the relations in the Grothendieck group of an Artin algebra are generated by the ones given by almost-split sequences precisely when the algebra is of finite representation type.  This result was generalized to $\Hom{}$-finite, Krull-Schmidt exact categories with enough projectives by H.~Enomoto in~\cite{Enomoto}, and to $\Hom{}$-finite, Krull--Schmidt triangulated categories with a cogenerator by J.~Haugland in~\cite{Haugland}. Inspired by these results, we will show in this Section that a similar statement holds (see \cref{thm:relations-g-vecteurs}) for the~$\b{g}$-vectors (or indices) of objects in a~$2$-Calabi--Yau triangulated category.  We will further generalize these results in Section~\ref{sec:extricats} to the setting of Ext-finite, Krull-Schmidt, extriangulated categories with Auslander--Reiten--Serre duality admitting projective objects with certain properties.
